Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-26 tex/results.tex
minor fix
many fixes, results subsection (b)

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main peaks presented in Rockstuhl et al.\ are 
successfully replicated. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

@@

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
resonant modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
and computing polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400-4800$ nm). These pillars are patterned on a squared 
grid with a pitch $P=L+500$ nm to reduce coupling. In both their simulations and experiments they 
perform polarized reflectance measurements with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

We first aim to replicate the computational result presented in Figure S4 of their supplementary 
material that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
a good candidate to replicate using \pygbe. Secondly, we will perform a second attempt of replication  
for the results presented in Figure 2a, in which they present reflectance measurements across wave number
for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
length of the pillars. This same case, counts with experimental results that we will use to attempt the validation of our solver.

\textbf{Difference between methods, mesh and dielectric data}

\textit{methods}

In Ellis et al. they run experiments using reflectance spectroscopy and they compute the solution of
Maxwell equations via the RF package of the finite element method software COMSOL. In their simulations 
they use periodic boundary conditions of one pillar over a portion of substrate, to represent the array of 
pillars and their interactions. 
We use the boundary element method in the quasistatic approximation, which is suitable in these case 
since the pillar's size is small compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). 
We measure extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots). 
The intensity of the peaks is not comparable, but we are looking to match the wave number (variable of interest) at which these events happen.

\textit{mesh}

For the case of aspect ratio $AR=4$ we count with a non-uniform triangular surface mesh (N=4398) provided by the authors of 
Ellis et al, which we use for validation and replication of FIgure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material we needed the remaining aspect ratio meshes. We generated uniform meshes using our
python script, and we determined the density of these meshes by comparing the extinction cross section for the case of AR=4 of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements (N=8564) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section where, on average, smaller than 3$\%$ and the variation on the wavelength peak
occurrence was smaller than 1 cm$^-1$. This analysis lead us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
the aspect ratio's variation study.

\textit{dielectric data}
The dielectric data for the simulations, was given by the authors of the paper via a private communication, 
and corresponds to experimental values of the dielectric.

\subsubsection{Replication of Figure S4 of supplementary material of Ellis et al. 2016}

To be able to replicate the result of Figure S4 of the supplementary material of Ellis et al, we
need to identify the lower frequency mode for each of
the aspect ratios in our computations. For each aspect ratio (AR) 
value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper) that is not a 
longitudinal mode. The longitudinal mode appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} show the results of the extinction 
cross section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm), for normal 
and 22 degrees angle of incidence. The simulations where performed 
for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
when having normal incidence as shown on see Figure \ref{fig:ellis_ang_inc}. From these results we select 
the lower mode that it is not a longitudinal one and extract its wavelength (see \ref{tab:ar_peaks}) to replicate 
\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al (digitized using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all
the cases.

Note: Ellis et al., changes the angle of incidence of the illuminating vector while in \pygbe we achieve this by
rotating the geometry instead.

@@

\subsubsection{Validation of \pygbe against Fig 2a experimental results, and replication of corresponfding computations}

The results of Figure 2a on Ellis et al. were obtained on a pillar of aspect ratio $AR=4$. For this case,
we count with the mesh provided by the authors. We also know that our computation 
for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
attempted to validate our simulations with their experimental results (red curve on paper), as well 
as to replicate their simulations (green curve on paper).
Figure 2a of Ellis et al, presents measured and simulated reflectance of SiC pillar
arrays with a 500 nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated size of the pillar.

Using \pygbe we compute the extinction cross section of an isolated SiC pillar (AR=4)
with no substrate, submerged in air under a constant electric field in the z-direction, 
and rotated the orientation of the pillar to match the angle of incidence used on Ellis et al. (see Figure \ref{fig:ellis_ang_inc}).
In Figure \ref{fig:pygbe_vs_exp_2a} we present a 
comparison of our simulations and the experimental results from Ellis et al. There is a 
difference in the peaks wavelength that is noticeable. This could be attributed to the
fact that in their experiments the separation between pillars is of 500 nm, which implies
there are coupling effects that in our simulations are not contemplated.

@@

\paragraph{First order correction}

Since our simulations do not count for coupling effects, we can not strictly imitate 
the conditions to validate our solver. However, from Figure S4 on the supplementary 
material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^-1$. Therefore, as a \textit{first order correction} we can 
subtract this value from our simulations to count for coupling effects. In Figure 
\ref{fig:val_2a} we present the result after applying the correction for coupling effects.
It is worth mentioning that the far left (837 cm$^-1$) and far right (964 cm$^-1$) peaks 
on Ellis results, are peaks associated with zone-folded LO (longitudinal) phonons, in 
particular P1 (837 cm$^-1$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
do not discuss this result into detail, but they explain that these peaks go beyond the scope of the work, 
they concentrate their analysis on the peaks that happen between 864–961 cm$^-1$

@@

If we use the same approximation and compare the results with Ellis simulations on
Figure 2 of their paper (green curve) we get (see Figure \ref{fig:rep_2a})

>>>>

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main resonance peaks presented in Rockstuhl et al.\ are 
closely matched. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

@@

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} studies the aspect-ratio evolution of high-order
modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
and computing polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400$--$4800$ nm). These pillars are patterned on a square 
grid with a pitch $P=L+500$ nm to reduce coupling. In both their simulations and experiments, they 
measured polarized reflectance with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

Our first aim was to replicate the computational result presented in Figure S4 of their supplementary 
material, corresponding to the black curve on their plot. In this 
figure, they show simulation results for the resonance spectral position of the lower-frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
a good candidate to replicate using \pygbe. [SAY WHY]
Our second attempted replication is  
for the results presented in Figure 2a, corresponding to reflectance measurements across wave number
for pillars with aspect ratio $AR=4$, angle of incidence of 22 degrees, and incoming polarization parallel to the 
length of the pillars. For this case, the authors also reported experimental results that we will use for validation of our solver.

\paragraph{Method:}
Ellis et al.\ ran experiments using reflectance spectroscopy and they computed the solution of
Maxwell's equations via the RF package of the finite element solver in the commercial software COMSOL. 
In their simulations, 
they used one pillar over a portion of substrate, with periodic boundary conditions to represent an array of 
pillars and their interactions. 
We use the boundary element method in the quasistatic approximation, which is suitable in this case 
since the pillar's size is small compared to the wavelength involved in the simulations (800--1000 cm$^{-1}$, which is 10000--12500 nm). 
We measure extinction cross section, which will express as peaks instead of depressions (shown in the reflection plots of Ellis et al.). 
The intensity of the peaks is not comparable, but we are looking to match the wave number (quantity of interest) at which these events happen.

\paragraph{Mesh:}
For the case with aspect ratio $AR=4$, we have a non-uniform triangular surface mesh ($N=4398$) provided to us by the authors of 
Ellis et al., which we used for validation and replication of Figure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
Python script, and we determined the density of these meshes by comparing the extinction cross section for the case with $AR=4$ of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements ($N=8564$) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
the aspect ratio variation study.

\paragraph{Dielectric data:}
The dielectric data for the simulations was given to us by the authors of the paper via a private communication, 
and corresponds to experimental values of the dielectric.

\subsubsection{Replication of Figure S4 in the supplementary materials of Ellis et al., 2016}

To be able to replicate the result of Figure S4 of the supplementary materials of Ellis et al., we
need to identify the lower-frequency mode for each of
the aspect ratios in our computations. For each aspect ratio ($AR$) 
value from 1 to 7, we computed the extinction cross section $C_{ext}$ across the wave numbers in the range
800--1000 $cm^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400$--$2800$ nm), for normal 
and 22-degrees angle of incidence. The simulations where performed 
for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
the lowest mode that it is not a longitudinal one and extracted its wavelength (see \ref{tab:ar_peaks}) to replicate 
\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
(Note that Ellis et al.\ changed the angle of incidence of the illuminating vector while in \pygbe we 
rotated the geometry instead.)

@@

\subsubsection{Validation of \pygbe against experimental results in Fig.\ 2a  of Ellis et al., and replication of the corresponding computations}

The results of Figure 2a in Ellis et al.\ were obtained on a pillar of aspect ratio $AR=4$. For this case,
we have the original mesh, provided to us by the authors. We also know that our computation 
for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
attempted to validate our simulations with their experimental results (red curve on their paper), as well 
as to replicate their simulations (green curve on their paper).
Figure 2a of Ellis et al., presents measured and simulated reflectances of SiC pillar
arrays with a 500 nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated size of the pillar.

Using \pygbe, we computed the extinction-cross section of an isolated SiC pillar ($AR=4$)
with no substrate, submerged in air under a constant electric field in the $z$-direction, 
and rotated the orientation of the pillar to match the angle of incidence used by Ellis et al.\ (see Figure \ref{fig:ellis_ang_inc}).
In Figure \ref{fig:pygbe_vs_exp_2a}, we present a 
comparison of our simulations and the experimental results of Ellis et al. A 
difference in the wavelengths of the peaks is noticeable. This may be attributed to the
fact that in their experiments the separation between pillars is of 500 nm, which implies
there are coupling effects that in our simulations are not considered.

@@

\paragraph{First-order correction.}

Since our simulations do not take into account coupling effects, we cannot strictly match 
the conditions to validate our solver. However, from Figure S4 in the supplementary 
materials of Ellis et al., we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^{-1}$. Therefore, as a \textit{first-order correction} we can 
subtract this value from our simulations to account for coupling effects. In Figure 
\ref{fig:val_2a}, we present the result after applying this correction for coupling effects.
It is worth mentioning that the far-left (837 cm$^{-1}$) and far-right (964 cm$^{-1}$) peaks 
on the results of Ellis et al., are peaks associated with zone-folded LO (longitudinal) phonons, in 
particular P1 (837 cm$^{-1}$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
do not discuss this result in detail, but they explain that these peaks go beyond the scope of the work; 
they concentrate their analysis on the peaks that happen between 864 and 961 cm$^{-1}$.
If we use the same approximation and compare the results with the simulations of Ellis et al.\ on
Figure 2 of their paper (green curve), we get Figure \ref{fig:rep_2a}.

@@
